Template for indicator documentation

### 2023-10-19 Nature_Index_product.Rmd
Update Nature_Index_product.Rmd
Set `eval = F` for saveRDS

```{r, include=F}
dir <- substr(getwd(), 1,2)
pData <- ifelse(dir == "C:", 
               "P:/41201785_okologisk_tilstand_2022_2023/data/",
               "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/")
saveRDS(CustomNI, paste0(pData, "cache/CustomNI.RDS"))
```

>>>>

```{r, include=F, eval=F}
dir <- substr(getwd(), 1,2)
pData <- ifelse(dir == "C:", 
               "P:/41201785_okologisk_tilstand_2022_2023/data/",
               "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/")
saveRDS(CustomNI, paste0(pData, "cache/CustomNI.RDS"))
```
